---
title: "Reproducible Research: Peer Assessment 1 by Werner Steinbeck"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r "Data Preprocessing"}
MyActiveDays <- read.csv("activity.csv")
# Tidy this up by getting the NA observations out
goodActivity <- complete.cases(MyActiveDays)
ActiveCases <-MyActiveDays[goodActivity, ]    # So the observations with data, no NA in here
# The date field is read as factors in different levels, need "real" dates here, so
z <- strptime(ActiveCases$date, "%Y-%m-%d")
```
## What is mean total number of steps taken per day?
### Total number of steps taken per day
```{r "Steps per Day"}

```
### Total number of steps taken per day - Graphically
If you do not understand the difference between a histogram and a barplot, research the difference between them. Make a histogram of the total number of steps taken each day
Calculate and report the mean and median of the total number of steps taken per day
```{r "Calculate Mean"}
# Sum of total steps measured divided by days of measurement
MeanTotalSteps <- sum(ActiveCases$steps)/length(unique(ActiveCases$date))
```
## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
